%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Projects}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}



%------------------------------------------------

\cventry
{leader of the team, 3rd highest score in class} % Job title
{Foody - A Restaurant Searching App} % Organization
{Web Development Course Project} % Location
{Apr. 2017 - June. 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
 \item Developed a Web App \& Mobile App using \textbf{React.js/Node.js/React Native}, hosted on AWS EC2. 
 \item Crawled 100K+ restaurant data from iPeen.com with \textbf{Python} BeautifulSoup toolkit.
 \item Utilized \textbf{PostgreSql} Database to handle data requests, deployed on AWS RDS.
\end{cvitems}
}


\cventry
{easily browse 20+yr old telnet bbs in a modern way} % Job title
{ModernPTT} % Organization
{Side Project} % Location
{May. 2020 - } % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
 \item \textbf{Built and offered} a set of APIs to interact with the BBS using \textbf{WebSocket} and \textbf{Node.js} 
 \item \textbf{Modernized} the browser interface with \textbf{ReactJS} and \textbf{MaterialUI}
\end{cvitems}
}

\cventry
{a database core written in java} % Job title
{VanillaDB} % Organization
{Database Course Project} % Location
{Feb. 2019 - June. 2019} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item \textbf{Speeded up} the monitoring system up to \textbf{16\%} by applying faster estimation algorithms.
\item \textbf{Implemented} a TPC-C testbench to \textbf{verify the correctness} of the system.  
\item \textbf{Applied and experimented} with four different \textbf{Cache Eviction Strategies} to enhance the performance by \textbf{8\%}.
\end{cvitems}
}

\cventry
{ranked top 10\%(7/65) in class} % Job title
{Parallel Computing} % Organization
{Class Competition} % Location
{Sep. 2018 - Jan. 2019} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
  \item \textbf{Deployed paralleled} Floyd-Warshall algorithm on a cluster using GPGPU, \textbf{performance ranked top 10\% in class}.
  \item \textbf{Achieved a 43\% speed up} by utilizing CPU's SIMD instructions on paralleled Bellman-Ford algorithm.
  \item Built a \textbf{MapReduce} Pipeline with \textbf{Apache Hadoop} to perform PageRank on 100GB of wikipedia pages to run in short time constraint. 
\end{cvitems}
}

\cventry
{achieved 800\% speed boost} % Job title
{Dirty Lens Recovering} % Organization
{Image Processing Course Project} % Location
{Sep. 2017 - Jan. 2018} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
  \item Implemented a \textbf{Machine Learning} RANSAC algorithm that removes dirty spots on a picture in Matlab.
  \item \textbf{Accelerated the process by 800\%} using Matlab CUDA Computing Toolbox.
\end{cvitems}
}

\end{cventries}